### 2018-01-26 study-dataset.tex
clustring first pass revised

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations.}
    \label{fig:ref-gof-maps}
\end{figure*}
% 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and component of motion (NS, EW, UD). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range, with outliers shown as scattered dots.}
    \label{fig:data-box-plot}
\end{figure}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations. The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}
% 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and component of motion (NS, EW, UD). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range, with outliers shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}
